On Secure Delegation of SampBQP with a Classical Client

### 2020-02-01 bqp.tex
Move QFHE to preliminary

\section{Constant-round blind delegation of BQP}

@@

\begin{algorithm}
	\caption{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	\begin{algorithmic}[1]
		\State The verifier runs $\mathsf{QHE.Keygen}(\lambda)$ to get $pk, sk$. \Ethan{Security param?}
		\State The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
		\State The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ to the prover
		\State The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
		\State The verifier decodes qubit-by-qubit \Ethan{hmm?}
		\State The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{algorithmic}
\end{algorithm}

>>>>

\section{Constant-Round Blind Delegation for BQP}

@@

\begin{algorithm}
	\caption{Blind Protocol for $\BQP$}
	\label{proto:BlindBQP}
	\begin{algorithmic}[1]
		\State The verifier runs $\mathsf{QHE.Keygen}(\lambda)$ to get $pk, sk$.
		\State The verifier encrypts $x$ to get $\mathsf{QHE.Enc}_{pk}(x)$
		\State The verifier sends $c=\mathsf{QHE.Enc}_{pk}(x)$ to the prover
		\State The prover sends $\mathsf{QHE.Eval}(\cF, c)$ to the verifier
		\State The verifier measures the incoming ciphertext according to \autoref{decodeMeasureOrder} and how it would've checked the $\QMA$ certificates
		\State The verifier decodes the measurement results
		\State The verifier uses $n$ copies to check for $x\in L$, and the other $n$ copies to check for $x\in\overline{L}$
	\end{algorithmic}
\end{algorithm}

### 2020-02-01 preliminaries.tex
Move QFHE to preliminary

\begin{dfn}
	A quantum homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

@@

@@

\floatname{algorithm}{Protocol}
\begin{algorithm}
	\caption{ $\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoIndCPA}
	\begin{algorithmic}[1]
		\State The challenge picks $b\in\set{0,1}$ at random
		\If{b=1}
			\State The challenger runs the protocol with the adversary, acting as the verifier with input $0^n$
		\Else
			\State The challenger runs the protocol with the adversary, acting as the verifier with input $x$
		\EndIf
		\State $\cA$ attempts to guess $b$
	\end{algorithmic}
\end{algorithm}
\floatname{algorithm}{Algorithm}

>>>>

We also use the quantum full homomorphic encryption (QFHE) scheme given in \cite{mahadev_qfhe} which allows the use of a classical client.

\begin{dfn}
	A homomophic encryption scheme is tuple of algorithms $\mathsf{HE}=(\mathsf{HE.Keygen}, \mathsf{HE.Enc}, \mathsf{HE.Dec}, \mathsf{HE.Eval})$ with the following descriptions:
	\begin{itemize}
		\item $\mathsf{Keygen}(1^\lambda)\rightarrow(pk, evk, sk)$
		\item $\mathsf{Enc}_{pk}(\mu)\rightarrow c$
		\item $\mathsf{Dec}_{sk}(c)\rightarrow \mu^*$
		\item $\mathsf{Eval}_{evk}(f, c_1, \ldots, c_l)\rightarrow c_f$
	\end{itemize}
\end{dfn}

@@

The constructions in \cite{mahadev_qfhe}, $\mathsf{QHE}=(\mathsf{QHE.Keygen}, \mathsf{QHE.Enc}, \mathsf{QHE.Dec}, \mathsf{QHE.Eval})$, has the following extra properties:
\begin{itemize}
	\item $\mathsf{QHE.Keygen}$ can be done classically.
	\item In the case where the plaintext is classical, $\mathsf{QHE.Enc}$ can be done classically.
\end{itemize}

Furthermore, one could either decode or measure first, in the following sense:
\begin{lemma}
	\label{decodeMeasureOrder}
	Let $\Lambda$ be a product of $X$ and $Z$ measurements. Then there exists $\Lambda'$ product of $X$ and $Z$ measurements and $\widehat{\mathsf{QHE.Dec}}$ a BPP algorithm so that
		$$\Lambda\circ\mathsf{QHE.Dec}=\widehat{\mathsf{QHE.Dec}}\circ\Lambda'$$
\end{lemma}
To the knowledgable reader, this is done simply by storing the so-called quantum-capable ciphertext also as qubits.

@@

\floatname{algorithm}{Protocol}
\begin{algorithm}
	\caption{ $\QPIP_1$ protocol for $\SampBQP$}
	\label{ProtoIndCPA}
	\begin{algorithmic}[1]
		\State The challenge picks $b\in\set{0,1}$ at random
		\If{$b=1$}
			\State The challenger runs the protocol with the adversary, acting as the verifier with input $0^n$
		\Else
			\State The challenger runs the protocol with the adversary, acting as the verifier with input $x$
		\EndIf
		\State $\cA$ attempts to guess $b$
	\end{algorithmic}
\end{algorithm}
\floatname{algorithm}{Algorithm}
